---
title: "HW 1 am5088"
author: Anika Mitchell
date: Sept 21, 2024
output:
  html_document:
      toc: true
      toc_float: true
      code_floating: hide
---

I'm an R Markdown document! 

# Problem 1
## Importing the dataset

Here's a **code chunk** that loads the 
a _penguins_ dataset:

```{r setup}
data("penguins", package = "palmerpenguins")

```
##Take a look at the data
```{r, include=FALSE}
tail(penguins)
```

```{r, message=FALSE}
skimr::skim(penguins)
```



## Dataset Description
The data in this dataset include 344 observations (rows) and 8 variables (columns) including the species (Adelie, Gentoo, Chinstrap), island (Torgersen, Biscoe, Dream), bill length (in mm), bill depth (in mm), flipper length (in mm), body mass (in g), sex, and year of penguins.

The mean flipper length is 201 mm. 

# Data Visualization

## Scatterplot
this code chunk creates a data frame and generates a plot
```{r scatterplot, echo=TRUE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```



I can take the mean of the sample, too!