---
title: "HW 1 am5088"
author: Anika Mitchell
date: Sept 21, 2024
output:
  html_document:
      toc: true
      toc_float: true
      code_floating: hide
---

The following problems are for HW1

# Problem 1
## Importing the dataset

Here's a **code chunk** that loads the 
a _penguins_ dataset:

```{r setup}
data("penguins", package = "palmerpenguins")
```
## Take a look at the data
```{r, include=FALSE}
tail(penguins)
```

```{r, message=FALSE}
skimr::skim(penguins)
```



## Dataset Description
The data in this dataset include 344 observations (rows) and 8 variables (columns) including the species (Adelie, Gentoo, Chinstrap), island (Torgersen, Biscoe, Dream), bill length (in mm), bill depth (in mm), flipper length (in mm), body mass (in g), sex, and year of penguins.

The mean flipper length is 201 mm. 

# Data Visualization

## Scatterplot
this code chunk creates a data frame and generates a plot
```{r scatterplot, echo=TRUE}
library(ggplot2) 
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)

```

# Problem 2

This code chunk creates a random sample of size 10 from a standard Normal distribution:
```{r}
x = rnorm(10)
```

This code chunk creates a data frame comprised of the following:

* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r problem2_df, message=FALSE}
library(tidyverse)
df_problem2s= tibble(
  vec_numeric = x,
  vec_logical = (x>0), 
  vec_char = c("My", "name", "is", "Anika", "and", "I", "love", "coding", "in", "R"),
  vec_factor = factor(c("lvl1", "lvl2", "lvl3", "lvl3", "lvl2", "lvl1", "lvl3", "lvl2", "lvl3", "lvl1" )) 
)
```

this code chunk shows how we take the mean:

```{r mean}
mean(df$vec_logical)
mean(pull(df,vec_char))
mean(df$vec_factor)
```

